\chapter{Lecture 6: Power Series}

\section{Introduction}
\begin{definition}
    [Power Series]
    A power series in $z$ is a n infinite series of the form:
    $$\sum_{n=0}^{\infty} a_n (z-z_0)^n$$
    where $a_n$ are complex numbers, $z$ is a complex variable, and $z_0 \in \mathbb{C}$ is the centre.
\end{definition}

\begin{theorem}
    [Absolute Convergence of Power Series]
    Suppose $\exists z_1 \neq z_0 | \sum_{n=0}^{\infty} a_n (z_1-z_0)^n$ converges. Then for each $z \in \mathbb{C} : |z-z_0| < |z_1 - z_0|$, the series $\sum_{n=0}^{\infty} a_n (z-z_0)^n$ converges \textbf{absolutely}.
\end{theorem}

\begin{proof}
    Since $\sum_{n=0}^{\infty} a_n (z_1-z_0)^n$ converges, we know:
    \begin{equation}\lim_{n \to \infty} a_n (z_1-z_0)^n = 0 \label{eq:1}\end{equation}
    \textit{so}: $|a_n| |z_1 - z_0|^n \leq M \forall n$ as $n \to \infty$.\\
    by \ref{eq:1}, $\exists N \in \mathbb{N} | n \geq N \implies |a_n| |z_1 - z_0|^n \leq 1$.\\
    So
    \begin{align*}
        |a_n| |z-z_0|^n & = \frac{|a_n||z_1 - z_0}{|z_1 - z_0|} |z-z_0|^n \\ & \leq M
    \end{align*}
    Let $\rho = \frac{|z-z_0|}{|z_1 - z_0|} < 1$. So
    \begin{align*}
        \sum_{n=0}{\infty} |a_n||z-z_0| \leq M \sum_{n =0}^{\infty}\rho^n
    \end{align*}
    Since $\rho < 1$, the geometric series $\sum_{n=0}^{\infty} \rho^n$ converges. Hence so does $\sum_{n=0}^{\infty} |a_n||z-z_0|^n$.\\
    \textbf{Absolute Convergence}
\end{proof}

\begin{definition}
    [Absolute Convergence]
    A series $\sum_{n=0}^{\infty} a_n$ is said to converge absolutely if $\sum_{n=0}^{\infty} |a_n|$ converges.
\end{definition}

\begin{definition}
    [Radius of Convergence]
    The radius of convergence of a power series $\sum_{n=0}^{\infty} a_n (z-z_0)^n$ is the number $R$ such that the series converges absolutely for $|z-z_0| < R$ and diverges for $|z-z_0| > R$. \\
    There are three possibilities:
    \begin{enumerate}
        \item Converges only for $z = z_0$ (i.e. $R = 0$)
        \item Converges for all $z \in \mathbb{C}$ (i.e. $R = \infty$)
        \item Converges for some $z \neq z_0$ (i.e. $0 < R < \infty$)
    \end{enumerate}
\end{definition}

\begin{lemma}
    Assume $z^\prime, z^{\prime\prime} \in \mathbb{C}$ are points such that:
    \begin{itemize}
        \item $\sum_{n=0}^{\infty} a_n (z^\prime - z_0)^n$ converges
        \item $\sum_{n=0}^{\infty} a_n (z^{\prime\prime} - z_0)^n$ diverges
    \end{itemize}

    There is a unique $R > 0$ such that:
    \begin{itemize}
        \item If $|z - z_0| < R$, then $\sum_{n=0}^{\infty} a_n (z - z_0)^n$ converges
        \item if $|z - z_0| > R$, then $\sum_{n=0}^{\infty} a_n (z - z_0)^n$ diverges
    \end{itemize}
    $R$ is called the radius of convergence.
\end{lemma}

\begin{remark}
    The behaviour o on the circle of convergence $|z - z_0| = R$ can be complicated! The series may converge or diverge, or both (depending on where on the circle you are).
\end{remark}

\section{Computing the Radius of Convergence}

\begin{theorem}
    Suppose $\sum_{n=0}^{\infty} a_n (z - z_0)^n$ is a power series with radius of convergence $ 0 < R \leq \infty$. Then:
    \begin{enumerate}
        \item $\frac{1}{R} = \lim_{n \to \infty}\left| \frac{a_{n+1}}{a_n} \right|$
        \item If $\lim_{n \to \infty} \root{n}\of{|a_n|}  = L$ exists, then $R = \frac{1}{L}$
    \end{enumerate}
\end{theorem}

\begin{proof}
    Assume
    \begin{align*}
        \exists \lim_{n \to \infty}\left| \frac{a_{n+1}}{a_n} \right| & = L
    \end{align*}

    Then:
    \begin{align*}
        \lim_{n \to \infty}\left| \frac{(z-z_0)^{n+1}a_{n+1}}{(z-z_0)^n a_n} \right| = |z - z_0 | L
    \end{align*}

    if $|z - z_0|L< \frac{1}{L}$, then $|z - z_0| L < 1$ and the series converges by the ratio test, and if $|z - z_0|L > \frac{1}{L}$, then the series diverges by the ratio test.\\

    Similarly, if $\lim_{n \to \infty} \root{n}\of{|a_n|} = L$ exists, then:
    \begin{align*}
        \lim_{n \to \infty} \root{n}\of{|a_n (z - z_0)^n|} & = |z - z_0| L
    \end{align*}
    If $|z - z_0|L < 1 \to R = |z - z_0| < \frac{1}L$, then the series converges by the root test, and if $|z - z_0|L > 1$, then the series diverges by the root test.
\end{proof}

\begin{remark}
    If $\lim_{n \to \infty}\left| \frac{a_{n+1}}{a_n} \right|$ does not exist, then $R = 0$
\end{remark}